Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-01 popl24/composition.tex
checkpoint

\begin{lemma}[Decode Composition]
  \label{lemma-decode}
Given well-typed $\prog_1;E[\mathit{decode}(g,v)]$ and certified $\mathit{decode}$ where 
$$
\config{\prog_1}{E[\ttt{decode}(g,v)]} \redxs \config{\prog_1;\prog_2}{E[\be]}
$$
If the following preconditions hold:
\begin{enumerate}
\item $g \not\in \cap \wired(\prog_1)$
\item $\gc{\progd(\prog_1)}{v}{\owl(g)}$
\end{enumerate}
then we have as postcondition:
\begin{enumerate}
  \item $\sep{\progd(\prog_1;\prog_2)}{\vdefs(\prog_1)}{\vdefs(\prog_2)}$
\end{enumerate}
\end{lemma}
Given the above, we can establish that any circuit built with certified
components is passive secure. 
\begin{theorem}
  \label{theorem-ygc-NIMO}
  If $e$ is a well-typed circuit definition using certified components
  where no gate output is wired more than once, and $\config{\varnothing}{e}
  \redxs \config{\prog}{\varnothing}$, then $\NIMO(\prog)$. 
\end{theorem}

@@

>>>>

\begin{lemma}[Decode Composition]
  \label{lemma-decode}
Given well-typed $\prog_1;E[\mathit{decode}(g,v)]$ and certified $\mathit{decode}$ where 
$$
\config{\prog_1}{E[\ttt{decode}(g,v)]} \redxs \config{\prog_1;\prog_2}{E[\be]}
$$
If the following preconditions hold:
\begin{enumerate}
\item $g \not\in \cap \wired(\prog_1)$
\item $\gc{\progd(\prog_1)}{v}{\owl(g)}$
\end{enumerate}
then we have as postcondition:
\begin{enumerate}
  \item $\sep{\progd(\prog_1;\prog_2)}{\vdefs(\prog_1)}{\vdefs(\prog_2)}$
\end{enumerate}
\end{lemma}
Given the above, we can establish that any circuit built with certified
components is passive secure. 
\begin{theorem}
  \label{theorem-ygc-NIMO}
  If $e$ is a well-typed YGC circuit definition using certified components
  where no gate output is wired more than once, and $\config{\varnothing}{e}
  \redxs \config{\prog}{\varnothing}$, then $\NIMO(\prog)$. 
\end{theorem}

@@

\subsection{Compositional Properties of GMW}

\input{gmw}

\begin{definition}[GMW Gate Certification]
  \label{definition-gmwgate-certification}
  Let $\mathit{gate}$ be a gate function and let $e$ be the following
  $\metaprot$ program:
  $$
  \begin{array}{l}
    \ttt{let in1 = \{c1 = flip[1,s11];c2 = flip[2,s12]\} in}\\
    \ttt{let in2 = \{c1 = flip[1,s21];c2 = flip[2,s22]\} in}\\
    \mathit{gate}\ttt{(g,in1,in2)}
  \end{array}
  $$
  and let $
  \config{\varnothing}{e}\redxs\config{\prog}{\ttt{\{c1 = v[1,gout]; c2 = v[2,gout]\}}}
  $.
  Then $\mathit{gate}$ is \emph{certified} iff both of the following conditions hold:
  \begin{enumerate}
  \item $\sep{\progtt(\prog)}{\ttt{\{flip[1,s11],flip[1,s21]\}}}{\ttt{\{v[2,gout]\}}}$
  \item $\sep{\progtt(\prog)}{\ttt{\{flip[2,s12],flip[2,s22]\}}}{\ttt{\{v[1,gout]\}}}$
  \end{enumerate}
\end{definition}

\begin{lemma}[GMW Gate Composition]
  \label{lemma-compose-gmw}
  Given well-typed $\prog_1;E[\mathit{gate}(\ttt{g},v_1,v_2)]$ and certified $\mathit{gate}$ where:
  $$
  \begin{array}{lcr}
   v_1 &\defeq& \ttt{\{c1 = v[1,g1out]; c2 = v[2,g1out]\}}\\
   v_2 &\defeq& \ttt{\{c1 = v[1,g2out]; c2 = v[2,g2out]\}}
  \end{array}
  $$
  and:
  $$
  \config{\prog_1}{E[\mathit{gate}(\ttt{g},v_1,v_2)]} \redxs \config{\prog_1;\prog_2}{E[\ttt{\{c1 = v[1,gout]; c2 = v[2,gout]\}}]}
  $$
  Then the following postconditions hold:
  \begin{enumerate}
  \item $\sep{\progtt(\prog)}{\ttt{\{v[1,g1out],v[1,g2out]\}}}{\ttt{\{v[2,gout]\}}}$
  \item $\sep{\progtt(\prog)}{\ttt{\{v[2,g1out],v[2,g2out]\}}}{\ttt{\{v[1,gout]\}}}$
  \end{enumerate}
\end{lemma}

\begin{definition}[GMW Encode Certification]
  Let $\mathit{encode}$ be an encoding function, and let:
  $$
  \config{\varnothing}{\ttt{encode(s1,s2)}} \redxs
  \config{\prog}{\ttt{\{shares1 = }v_1\ttt{; shares2 = }v_2\ttt{\}}}
  $$
  where:
  $$
  \begin{array}{rcl}
    v_1 &=& \ttt{\{ c1 = v[1,s1out]; c2 = v[2,s1out] \}}\\
    v_2 &=& \ttt{\{ c1 = v[1,s2out]; c2 = v[2,s2out] \}}
  \end{array}
  $$
  Then $\mathit{encode}$ is \emph{certified} iff each of the following conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
  \item $\sep{\progtt(\prog)}{\ttt{\{ s[1,s1] \}}}{\ttt{\{ v[2,s1out], v[2,s2out] \}}}$
  \item $\sep{\progtt(\prog)}{\ttt{\{ s[2,s2] \}}}{\ttt{\{ v[1,s1out], v[1,s2out] \}}}$
  \end{enumerate}
\end{definition}

\begin{theorem}
  \label{theorem-gmw-NIMO}
  If $e$ is a well-typed GMW circuit definition using certified
  components and $\config{\varnothing}{e} \redxs
  \config{\prog}{\varnothing}$, then $\NIMO(\prog)$.
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup (V \cup \outv)$. Noting that any encoding
  necessarily uses entirely fresh variables by Definition and type
  safety, by applying Lemmas \ref{lemma-compose-gmw} and
  \ref{lemma-wire-framing} and the frame rule of
  \cite{barthe2019probabilistic} we obtain:
  $$
  \sep{\progd(\prog)}{(S_{\{2\}}\cup\{\outv\})}{V_{\{1\}}}
  \quad \text{and} \quad \sep{\progd(\prog)}{(S_{\{1\}}\cup\{\outv\})}{V_{\{2\}}}
  $$
  That is, the marginal distribution of client 1's secrets and the output are independent
  of client 2's views, and vice-versa. The result follows. 
\end{proof}

### 2023-07-01 popl24/main.tex
checkpoint

\title{Automating MPC Security}

@@

\begin{abstract}
  We show how to formulate a sound hyperproperty of MPC passive security, and how this
  supports automated verification.
\end{abstract}

@@

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

>>>>

\title{Automating Verification of MPC Security: $\metaprot$ to $\minifed$}

@@

\begin{abstract}
  We formulate a sound hyperproperty of MPC passive security and show how this
  supports automated and semi-automated verification.
\end{abstract}

@@

\input{intro}

@@

\input{bruteforce}

\input{metalang}

\input{composition}

\bibliographystyle{ACM-Reference-Format}
\bibliography{logic-bibliography,secure-computation-bibliography}

### 2023-07-01 popl24/pmf.tex
checkpoint

\subsection{Basic Definitions} We begin by defining memory probability distributions as follows.
\begin{definition}
  A \emph{memory probability distribution} $\pdf{X}$ is a function
  mapping memories in $\mems(X)$ to values in $[0..1]$, such that:
  $$
  \sum_{\store \in \mems(X)} \pdf{X}(\store) \  = \ 1
  $$
  We call $X$ the \emph{domain} of $\pdf{X}$.
\end{definition}
To recover succinct and familiar notation, we may omit the domain of a
distribution when it is clear from an application context-
i.e., we allow the following sugaring:
$$
\pdf{}(\store) \defeq \pdf{\dom(\store)}(\store)
$$
Now, we can define a notion of marginal and conditional
distributions as follows, which are standard for discrete
probability mass functions. 
\begin{definition}
  Given $X$ the \emph{marginal distribution} of $Y \subseteq X$
  in a distribution $\pdf{X}$, denoted $\margd{\pdf{X}}{Y}$,
  is a distribution with domain $Y$ where for all
  $\store \in \mems(Y)$:
  $$
  (\margd{\pdf{X}}{Y})(\store) =
  \sum_{\store' \in \mems(X-Y)} \pdf{X}(\store \cap \store')
  $$
\end{definition}

>>>>

\subsection{Basic Definitions} We begin by defining memory probability distributions as follows.
\begin{definition}
  A \emph{memory probability distribution} $\pdf{X}$ is a function
  mapping memories in $\mems(X)$ to values in $[0,1]$, such that:
  $$
  \sum_{\store \in \mems(X)} \pdf{X}(\store) \  = \ 1
  $$
  We call $X$ the \emph{domain} of $\pdf{X}$.
\end{definition}
To recover succinct and familiar notation, we may omit the domain of a
distribution when it is clear from an application context-
i.e., we allow the following sugaring:
$$
\pdf{}(\store) \defeq \pdf{\dom(\store)}(\store)
$$
Now, we can define a notion of marginal and conditional
distributions as follows, which are standard for discrete
probability mass functions. 
\begin{definition}
  Given $X$ the \emph{marginal distribution} of $Y \subseteq X$
  in a distribution $\pdf{X}$, denoted $\margd{\pdf{X}}{Y}$,
  is a distribution with domain $Y$ where for all
  $\store \in \mems(Y)$:
  $$
  (\margd{\pdf{X}}{Y})(\store) =
  \sum_{\store' \in \mems(X-Y)} \pdf{X}(\store \cap \store')
  $$
\end{definition}
